Tweedie in TMB

### 2019-05-14 analysis/resources/simple-sdmTMB.Rmd
move exploratory code to analysis/resources

---
title: "Binomial TMB"
output: html_notebook
---

>>>>

---
title: "Practice TMB"
output: html_notebook
---

```{r setup}
    knitr::opts_knit$set(root.dir = normalizePath("/Users/capitan/github/dfo/gfranges/")) 
library(sdmTMB)

Load data from cache

```{r}
d <- readRDS("data-cache/pacific-cod.rds")
d$density <- d$density_kgpm2
```

```{r}
# Gaussian:
pcod_gaus <- subset(d, density > 0 & year >= 2013)

pcod_spde_gaus <- make_spde(pcod_gaus$X, pcod_gaus$Y, n_knots = 50) #need to calculate X and Y (utms?)
m_pos <- sdmTMB(pcod_gaus,
  log(density) ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
  time = "year", spde = pcod_spde_gaus)

### 2019-05-14 analysis/resources/tweedie-TMB.Rmd
move exploratory code to analysis/resources

```{r set-up}
## Load TMB TRUE
library(TMB)
library(tweedie)

@@

```{r}
## Data and parameters
data <- list(y = y, x = x)
parameters <- list(a=0, b=0, log_phi = log(1), p = 0 )

@@

plot(a_profile)
plot(b_profile)

```

@@

```{r}
# function to generate negative log-likelihood for a parameter value
nll_tweedie <- function(par) {
  eta <- par[1] + par[2] * x
  mu <- exp(eta)
  p <- plogis(par[3]) + 1
  phi <- exp(par[4])
  # sum of negative log likelihoods:
  loglik <- log(dtweedie(y, power = p, mu = mu, phi = phi))
  nll <- -sum(loglik) #[is.finite(loglik)]
  print(nll)
  nll
}

tweedie_ml <- nlminb(start = c(a = 0, b = 0, ipx = 0, log_phi = log(1)), nll_tweedie)
tweedie_ml$par 
```

@@

```{r}
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
sdr$par.fixed
tweedie_ml$par 
```

>>>>

```{r set-up}
## Load TMB 
library(TMB)
library(tweedie)

@@

```{r}
## Data and parameters
data <- list(y = y, x = x)
parameters <- list(a=0, b=0, p = 0, log_phi = log(1) )

@@

plot(a_profile)
plot(b_profile)
```

@@

```{r}
# function to generate negative log-likelihood for a parameter value
nll_tweedie <- function(par) {
  eta <- par[1] + par[2] * x
  mu <- exp(eta)
  phi <- exp(par[4])
  power <- plogis(par[3]) + 1
  # sum of negative log likelihoods:
  loglik <- log(dtweedie(y, power = power, mu = mu, phi = phi))
  nll <- -sum(loglik) #[is.finite(loglik)]
  print(nll)
  nll
}

tweedie_ml <- nlminb(start = c(a = 0, b = 0,  logis_p = 0, log_phi = log(1)), nll_tweedie)
tweedie_ml$par 
```

@@

```{r}
library(statmod)
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
sdr$par.fixed
tweedie_ml$par 
```
